FTLR proof cases

### 2018-03-09 fully-abstract-comp/ftlr-proof-cases.tex
Some comments, proposed generalized antireduction lemma.

\begin{lemma}[Steps-to termination]
  For all $\Phi_S$, $\Phi_T$, $\Phi_T'$, $j$, $n$, if
\[
  \Phi_T \steps[j] \Phi_T' \text{ and } \npair{(\Phi_S,\Phi_T')} \in \lro,
\]
then
\[
  \npair{(\Phi_S,\Phi_T)} \in \lro
\]
\end{lemma}

@@

\subsubsection*{Assuming target machine terminates}
\paragraph{Case: }
In the case  is the first step of the execution,

>>>>

\begin{lemma}[$\lro$ closed under target language antireduction]
  For all $\Phi_S$, $\Phi_T$, $\Phi_T'$, $j$, $n$, if
\[
  \Phi_T \steps[j] \Phi_T' \text{ and } \npair{(\Phi_S,\Phi_T')} \in \lro,
\]
then
\[
  \npair{(\Phi_S,\Phi_T)} \in \lro
\]
\end{lemma}

\dominique{9-3-2018: the below is a proposed generalisation of the above antireduction lemma  that I expect will hold (based on experience with similar LRs in the past).}
\begin{lemma}[$\lro$ closed under antireduction (generalised previous lemma)]
  For all $\Phi_S$, $\Phi_S'$, $\Phi_T$, $\Phi_T'$, $j_S,J_T$, $n$, if
  \begin{itemize}
  \item $\Phi_S \steps[j_S] \Phi_S'$
  \item $\Phi_T \steps[j_T] \Phi_T'$
  \item $\npair{(\Phi_S',\Phi_T')} \in \lro$
\end{itemize}
then
\[
  \npair[n+\min(j_S,j_T)]{(\Phi_S,\Phi_T)} \in \lro
\]
\end{lemma}

@@

\subsubsection*{Assuming target machine terminates}
\dominique{I suspect it would be more economical to not treat this case separately from the above (source machine terminates), but rather prove both results simultaneously by induction on the length of the terminating execution.}
\paragraph{Case: }
In the case  is the first step of the execution,
